---
title: "P-matrix / PCA"
output:
  html_document:
    df_print: paged
  html_notebook:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

In this notebook I am creating code to run the analysis described in Felman (1995) to obtain valence and arousal focus scores. 

I am using a subset of existing data (taken from EMG study). 

The steps fopr extracting the values are as follows. 

  1. Get p-matrix between emotion terms for each participant 
  2. Apply a principle axis factor analysis to each p-matrix
  3. Apply tucker congruence coefficient to previously derived factors/Decide on valence and arousal factors
  4. The percentage of variance explained for the valenc and arousal factors give an index of valence and arousal focus. 

```{r message = FALSE}
library(tidyverse)
library(psych)
library(FactoMineR)
```

First I will read in the test data

```{r message = FALSE, warning = FALSE}
test_data <- read_csv(here::here("data", "test_data.csv")) %>% 
  tidyr::separate(col = trialunique, 
                  into = c("id", "trial", "rep"),
                  sep = "_") %>% 
  mutate(trial_ref = glue::glue("{trial}_{rep}"), 
         id = as.numeric(id)) %>% 
  drop_na(id) %>% 
  janitor::clean_names()

visdat::vis_dat(test_data)
```
<br>
## Extracting the two factors 

I want to extract the factor structure for each participant. So I will created a nested dataframe that contains their emotion scores 

```{r nesteddataframe}

emotion_select <- test_data %>% 
  select(id, tas, depression, active_rating:tender_rating) 

emotion_select

nested_ratings <- emotion_select %>% 
  nest(ratings = c(active_rating:tender_rating))

nested_ratings

valence_accounted_fun <- function(df){
  psych::fa(r = df, nfactor = 2, rotate = "none", fm = "pa")$Vaccounted[2, 1]
}

possibly_valence <- possibly(valence_accounted_fun, otherwise = NA)

arousal_accounted_fun <- function(df){
  psych::fa(r = df, nfactor = 2, rotate = "none", fm = "pa")$Vaccounted[2, 2]
}

possibly_arousal <- possibly(arousal_accounted_fun, otherwise = NA)



affect_fa <- nested_ratings %>% 
  mutate(valence_accounted = as.numeric(map(ratings, possibly_valence)), 
         arousal_accounted = as.numeric(map(ratings, possibly_arousal)), 
         valence_pct = valence_accounted * 100, 
         arousal_pct = arousal_accounted * 100)

visdat::vis_dat(affect_fa)

```



So now that i have the function working I want to esimate the regression coefficents. But first I would like 
to check normality
```{r}

par(mfrow = c(2,2))

for (i in c("tas", "depression", "arousal_pct", "valence_pct")){ 
  tmp_dat <- affect_fa[[i]]
  tmp <- hist(tmp_dat,
              main = paste("Histogram of", i)) 
  print(tmp)
}

par(mfrow = c(1,1))


```

```{r}
a_a_lm <- lm(arousal_pct~tas, 
   data = affect_fa) 
a_d_lm <- lm(arousal_pct~depression, 
   data = affect_fa) 
a_a_d_lm <- lm(arousal_pct~tas+depression, 
   data = affect_fa)

sjPlot::tab_model(a_a_lm, a_d_lm, a_a_d_lm, 
                  show.ci = TRœUE) 

v_a_lm <- lm(valence_pct~tas, 
   data = affect_fa) 
v_d_lm <- lm(valence_pct~depression, 
   data = affect_fa) 
v_a_d_lm <- lm(valence_pct~tas+depression, 
   data = affect_fa) 


```



